Transferability of clinical prediction models for early trauma care

### 2019-06-18 ManuscriptMarkdown.Rmd
Update ManuscriptMarkdown.Rmd

  **Results:** `r total.number.of.patients ` patients were included. Model
  validation median mistriage rate with 95% UI ranged from `r
  lowest.val.mistriage` to `r highest.val.mistriage`. and transferred model
  mistriage rate ranged from `r lowest.tran.mistriage` to `r
  highest.tran.mistriage` across all samples. Worst performance after transfer
  compared to receiving sample validation performance was found in the `r
  colnames(highest.comp.mistriage)` sample with a median mistriage difference of
  `r highest.comp.mistriage`.

@@

# Materials and methods
## Study design
We conducted a registry-based cohort study. Sweden has a nationally encompassing
register for registering trauma called SweTrau. SweTrau data was used to create
clinical prediction models, which were transferred between different contexts to
study the effects on mistriage. The study and analysis plans were made
publically available before the research was undertaken (Add reference to github
repo here).

@@

Data was obtained from SweTrau between 2011 and 2016. Today 95,5% (52 of 55) of
Swedish hospitals record trauma cases in SweTrau. Currently the registry
includes 55 000 cases, and the board encourages its use in both academic
research and more local quality improvement initiatives [@RN28].

@@

### Model development
In the model development step a clinical prediction model was developed in the
high-volume centre development sample. The model was developed using logistic
regression as implemented in the R function glm. The dependent variable was all
cause mortality within 30 days of trauma and independent variables SBP, RR, and
GCS modelled as previously described. To avoid overfitting the model we used a
bootstrap procedure to estimate a linear shrinkage factor that we then applied
to the model coefficients [@RN61]. The shrunk model was then used to estimate
the probability of all cause 30-day mortality in the development sample. A
gridsearch was performed across estimated probabilities in the development
sample to identify the cut-off that optimised overtriage keeping undertriage at
less than 5% [@RN39]. This cut-off was then used to classify patients as major
or minor trauma.

>>>>

  **Results:** `r total.number.of.patients ` patients were included. Model
  validation median mistriage rate with 95% UI ranged from `r
  lowest.val.mistriage` to `r highest.val.mistriage`, and transferred model
  mistriage rate ranged from `r lowest.tran.mistriage` to `r
  highest.tran.mistriage` across all samples. Worst performance after transfer
  compared to receiving sample validation performance was found in the `r
  colnames(highest.comp.mistriage)` sample with a median mistriage difference of
  `r highest.comp.mistriage`.

@@

# Materials and methods
## Study design
We conducted a registry-based cohort study. Sweden has a nationally encompassing
register for registering trauma called SweTrau. SweTrau data was used to create
clinical prediction models, which were transferred between different contexts to
study the effects on mistriage. The study and analysis plans were made
publically available before the research was undertaken [@RN59].

@@

Data was obtained from SweTrau between 2011 and 2016. Today 95,5% (52 of 55) of
Swedish hospitals record trauma cases in SweTrau. Currently the registry
includes 55 000 cases, and the board encourages its use in both academic
research and local quality improvement initiatives [@RN28].

@@

### Model development
In the model development step a clinical prediction model was developed in the
high-volume centre development sample. The model was developed using logistic
regression as implemented in the R function glm. The dependent variable was all
cause mortality within 30 days of trauma and independent variables SBP, RR, and
GCS modelled as previously described. To avoid overfitting the model a
bootstrap procedure was used to estimate a linear shrinkage factor that was then applied
to the model coefficients [@RN61]. The shrunk model was then used to estimate
the probability of all cause 30-day mortality in the development sample. A
gridsearch was performed across estimated probabilities in the development
sample to identify the cut-off that optimised overtriage keeping undertriage at
less than 5% [@RN39]. This cut-off was then used to classify patients as major
or minor trauma.
